An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-26 EconGrowth2.Rnw
Added commented options for gathering CES spaghetti data from different archives.

<<CES_Spaghetti_Graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$) nesting (without energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
createCESSpaghettiGraph(energyType=NA)
@

@@

<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$)$e$ nesting (with energy). Only 50 resample models are shown. **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
@

<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($le$)$k$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
createCESSpaghettiGraph(energyType="Q", nest="(le)k")
@

<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($ek$)$l$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. ****">>=
# createCESSpaghettiGraph(energyType="Q", nest="(ek)Le", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(ek)l", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
@

>>>>

<<CES_Spaghetti_Graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$) nesting (without energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. Need to plot fit to historical data as a red line. ****">>=
createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType=NA, archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
# createCESSpaghettiGraph(energyType=NA)
@

@@

<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($kl$)$e$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. Need to plot fit to historical data as a red line. ****">>=
createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(kl)e", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(kl)e")
@

<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($le$)$k$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. Need to plot fit to historical data as a red line. ****">>=
createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(le)k", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(le)k")
@

<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Indexed GDP predictions for 1000 CES resample models for the ($ek$)$l$ nesting (with energy). **** Need to change the order of the countries to correspond to countryAbbrevsForGraph. Need to plot historical data as open circles instead of red lines. Need to plot fit to historical data as a red line. ****">>=
createCESSpaghettiGraph(energyType="Q", nest="(ek)Le", archive="data_archive/data_resample_2013-11-16_Best_Algorithm_Saving_Models_n=50.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(ek)l", archive="data_archive/data_resample_2013-11-19_Best_Algorithm_Saving_Models_Massively_Parallel_n=1000.zip")
# createCESSpaghettiGraph(energyType="Q", nest="(ek)l")
@
